---
title: "How to work with VisuNet?"
output:
    html_document:
      css: style.css
---

***

### Input format
 
***


VisuNet is available for any rule-based classifier in supported data frame formats.

#### 'Line by line' format

Data should be expressed as a data frame and needs to contain the following columns:

* FEATURES - the left-hand side of the rule corresponds to comma-separated attributes and their values, type factor 
* DECISION - the right hand side of the rule corresponds to decision value, type factor
* ACC_RHS - the rule accuracy, type numeric 
* SUPP_RHS - the rule support, type numeric

A p-value ('PVAL') column is not obligatory.

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
library(VisuNet)
library(knitr)
library("kableExtra")
kable(autcon_ruleset[4:6,], format="html",  caption = "Sample 'line by line' data frame") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


You can use 'line by line' format with the option:
`type = 'L`


```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
rules = data(autcon_ruleset)
vis_out = visunet(rules, type = 'L')
```

#### R.ROSETTA output

The rules data frame that is the output of R.ROSETTA can be directly run in VisuNet. See **?rosetta** from the [R.ROSETTA](https://github.com/komorowskilab/R.ROSETTA.git) package for details.

The R.ROSETTA output format can be use with the option:
`type = 'RDF` and this is the default variable.

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
#the rule-based model construction using R.ROSETTA
resultsRos <- rosetta(autcon)
vis_out = visunet(resultsRos$main, type = 'RDF')
```


### Run VisuNet

***

VisuNet is an R package 

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
require(VisuNet)

#Sample rule set for a classifier of autistic and non-autistic young males
#'Line by line' data type
data(autcon_ruleset)

#Run VisuNet
#Remember to click DONE once you finished your work with VisuNet
vis_out = visunet(autcon_ruleset, type = 'L')
```


### The interface

***


### VisuNet output

***


### Rule network customization

***
Rule networks are constructed using a [visNetwork](https://github.com/datastorm-open/visNetwork) package that enable to add/change node and edge properties according to our needs, e.g. change the color of nodes or the edge type according to the specific conditions. We are not limit to the existing variables in a rule network object, but we can add a new one that are implemented in [visNetwork](https://github.com/datastorm-open/visNetwork). See **?visNodes** and **?visEdges** for a full list of available options.