---
title: "How to work with VisuNet?"
output:
    html_document:
      css: style.css
---

***

### Input format
 
***


VisuNet is available for any rule-based classifier in supported data frame formats.

#### 'Line by line' format

Data should be expressed as data frame and needs to contain the following columns:

* FEATURES - the left-hand side of the rule corresponds to comma-separated attributes and their values, factor 
* DECISION - the right hand side of the rule corresponds to decision value, factor
* ACC_RHS - the rule accuracy, numeric 
* SUPP_RHS - the rule support, numeric

A p-value ('PVAL') calumn is not obligatory.

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
library(VisuNet)
library(knitr)
library("kableExtra")
kable(autcon_ruleset[4:6,], format="html",  caption = "Sample 'line by line' data frame") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


You can use 'line by line' format with the option:
``` type = 'L```


```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
rules = data(autcon_ruleset)
vis_out = visunet(rules, type = 'L')
```

#### R.ROSETTA output

Rule data frame that is the output of R.ROSETTA can be directly run in VisuNet. See **?rosetta** from the **R.ROSETTA** package for details.

The R.ROSETTA output format can be use with the option:
``` type = 'RDF```

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
resultsRos <- rosetta(autcon)
vis_out = visunet(resultsRos$main, type = 'RDF')
```

#### RGUI ROSETTA output



### Quick run

***

### The interface

***

### Rule network customization