---
title: "How to work with VisuNet?"
output:
    html_document:
      css: style.css
      theme:  cerulean
      highlight: pygments
      toc: true
      toc_float:
        collapsed: true
      toc_depth: 3
---

***

# Input format
 

VisuNet is available for any rule-based classifier in supported data frame formats.

## 'Line by line' format

Data should be expressed as a data frame and needs to contain the following columns:

* FEATURES - the left-hand side of the rule corresponds to comma-separated attributes and their values, type factor 
* DECISION - the right hand side of the rule corresponds to decision value, type factor
* ACC_RHS - the rule accuracy, type numeric 
* SUPP_RHS - the rule support, type numeric

A p-value ('PVAL') column is not obligatory.

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
library(VisuNet)
library(knitr)
library("kableExtra")
kable(autcon_ruleset[4:6,], format="html",  caption = "Sample 'line by line' data frame") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


You can use 'line by line' format with the option:
`type = 'L`


```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
rules <- data(autcon_ruleset)
vis_out <- visunet(rules, type = 'L')
```

## R.ROSETTA output

The rules data frame that is the output of R.ROSETTA can be directly run in VisuNet. See **?rosetta** from the [R.ROSETTA](https://github.com/komorowskilab/R.ROSETTA.git) package for details.

The R.ROSETTA output format can be use with the option:
`type = 'RDF` and this is the default variable.

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
#the rule-based model construction using R.ROSETTA
resultsRos <- rosetta(autcon)
vis_out <- visunet(resultsRos$main, type = 'RDF')
```

***
# Run VisuNet


VisuNet is an R package 

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
require(VisuNet)

#Sample rule set for a classifier of autistic and non-autistic young males
#'Line by line' data type
data(autcon_ruleset)

#Run VisuNet
#Remember to click DONE once you finished your work with VisuNet
vis_out <- visunet(autcon_ruleset, type = 'L')
```

***
# The interface



***
# VisuNet output



***
# Rule network customization


Rule networks are constructed using a [visNetwork](https://github.com/datastorm-open/visNetwork) package that enable to add/change node and edge properties, e.g. change the color of nodes or the edge type according to the specific conditions. We are not limited to the existing variables in a rule network object, but we can add new ones that are implemented in [visNetwork](https://github.com/datastorm-open/visNetwork). See **?visNodes** and **?visEdges** for a full list of available options.

## Nodes customization

We identified 11 genes previously reported in databases of autism associations: [SFARI](https://gene.sfari.org/), [AutDB](http://autism.mindspec.org/autdb/Welcome.do) and [ASD](http://asd.princeton.edu). We would like to mark that genes as stars. The example shows how to do this:

```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
#genes reported in databases of autism associations
aut_genes <- c('TSPOAP1', 'COX2','NCS1','RHPN1','FLRT2',
              'BAHD1','NCKAP5L','PPOX', 'NGR2',
              'ATXN8OS','DEPDC1')

#create the new variable that contains nodes information for 'all' decisions
nodes_RNO <- vis_out$all$nodes

#create the new vector of variables: shape. 'dot' is the default shape of nodes
nodes_RNO$shape <- rep('dot', length(nodes_RNO$label))

#mark selected genes as stars using the label attribute 
nodes_RNO$shape[which(as.character(nodes_RNO$label) %in% aut_genes)] <- 'star'

#create the node object list
nodesL <- list(nodes = nodes_RNO,CustCol =  c('shape'))

#rerun VisuNet with a new shape of nodes
vis_out2 <- visunet(autcon_ruleset, type = 'L', CustObjectNodes = nodesL)
```

To rerun VisuNet with the customized object for nodes,  you need to provide the original rule set and a list `CustObjectNodes` that contains the customized VisuNet object for nodes.
`CustObjectNodes` includes the customized object for nodes: `nodes` and a vector of column names that were changed/added to the object: `CustCol`.


```{r, echo = FALSE, warning=FALSE, fig.cap='Sample customized rule network for the autistic and non-autistic young males classifier from VisuNet. Marked genes reported in databases of autism associations (constructed for min Support=17 and min Accuracy=88%)'}
vis_out <- readRDS('data/visunet_out_nodes.RDS')
visNetwork(nodes = vis_out$nodes, edges = vis_out$edges, width = '100%')%>% 
  visLayout(randomSeed = 123) %>%
  visInteraction(hover = TRUE, navigationButtons = TRUE) %>%
  visOptions(selectedBy = list(variable = "group" , multiple = TRUE, main = "Select by decision", style = 'width: 200px; height: 30px;
                                                                padding-left: 80px;
                               font-size: 15px;
                               color: black;
                               border:none;
                               outline:none;'))
```


## Edges customization

Let's assume that COX2 controls MAP7 and we would like to show the edge direction on the rule network:


```{r, echo = TRUE, fig.align='center', warning=FALSE, eval=FALSE}
#mark the interaction between COX2 and MAP7 genes
edges_RNO <- vis_out$all$edges

#create the new vector of variables: arrows. 'enabled' is the default variable for edges
edges_RNO$arrows <- rep('enabled', length(edges_RNO$label2))

#add direction to selected edge using the label2 attribute 
edges_RNO$arrows[which(edges_RNO$label2 == 'COX2=3-MAP7=2')] <- 'to'

#create the edge object list
edgesL <- list(edges = edges_RNO,CustCol =   c('arrows'))

#rerun VisuNet with a new variable of edges
vis_out3 <- visunet(autcon_ruleset, type = 'L', CustObjectNodes = nodesL, CustObjectEdges = edgesL)
```

We are able to rerun VisuNet using customized object for edges by providing the original rule set and a list `CustObjectEdges` that contains the customized VisuNet object for edges. 
`CustObjectEdges` includes the customized object for edgess: `edges` and a vector of column names that were changed/added to the object: `CustCol`. 

We can rerun VisuNet using both customized objects: `CustObjectEdges` and `CustObjectNodes`.  


```{r, echo = FALSE, warning=FALSE, fig.cap='Sample customized rule network for the autistic and non-autistic young males classifier from VisuNet. Marked genes reported in databases of autism associations and the edge direction between COX2 and MAP7  (constructed for min Support=17 and min Accuracy=88%)'}
vis_out <- readRDS('data/visunet_out_edges.RDS')
visNetwork(nodes = vis_out$nodes, edges = vis_out$edges, width = '100%')%>% 
  visLayout(randomSeed = 123) %>%
  visInteraction(hover = TRUE, navigationButtons = TRUE) %>%
  visOptions(selectedBy = list(variable = "group" , multiple = TRUE, main = "Select by decision", style = 'width: 200px; height: 30px;
                                                                padding-left: 80px;
                               font-size: 15px;
                               color: black;
                               border:none;
                               outline:none;'))
```

